---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.path = "man/figures/README-",
  message = FALSE, warning = FALSE, error = FALSE, tidy = TRUE
)
```

# rockchain

[![Travis-CI Build Status](https://travis-ci.org/leonawicz/rockchain.svg?branch=master)](https://travis-ci.org/leonawicz/rockchain)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/leonawicz/rockchain?branch=master&svg=true)](https://ci.appveyor.com/project/leonawicz/rockchain)
[![Coverage Status](https://img.shields.io/codecov/c/github/leonawicz/rockchain/master.svg)](https://codecov.io/github/leonawicz/rockchain?branch=master)

The `rockchain` package provides simple interfaces to [coinmarketcap.com](https://coinmarketcap.com/) ticker and market cap data and [blockchain.info](https://blockchain.info/) ticker and Bitcoin wallet data. The current package does not yet support additional blockchain APIs, but will in the future. For now, it offers cryptocurrency market data retrieval and Bitcoin wallet transaction data retrieval via the two currently available APIs.

## Installation

You can install rockchain from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("leonawicz/rockchain")
```

## Example

```{r example}
library(rockchain)
cap()

w <- wallet("115p7UMMngoj1pMvkpHijcRdfJNXj6LrLn")
balance(w)
```

For more details see the [vignette](https://leonawicz.github.io/rockchain/articles/rockchain.html).
