---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.path = "man/figures/README-",
  message = FALSE, warning = FALSE, error = FALSE, tidy = TRUE
)
```

# rockchain

[![Travis-CI Build Status](https://travis-ci.org/leonawicz/rockchain.svg?branch=master)](https://travis-ci.org/leonawicz/rockchain)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/leonawicz/rockchain?branch=master&svg=true)](https://ci.appveyor.com/project/leonawicz/rockchain)
[![Coverage Status](https://img.shields.io/codecov/c/github/leonawicz/rockchain/master.svg)](https://codecov.io/github/leonawicz/rockchain?branch=master)

The `rockchain` package provides a simple interface to [blockchain.info](https://blockchain.info/) ticker and wallet data. At this time the package is very basic. It does not offer any additional functionality beyond basic wallet transaction data retrieval or integrate with other blockchain APIs. It currently only returns bitcoin data. Access to other cryptocurrencies in not yet implemented.

## Installation

You can install rockchain from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("leonawicz/rockchain")
```

